Binary Latent Representations for Efficient Ranking

### 2017-06-22 paper/paper.tex
Spelling fixes.

We speculate that binary representations are more useful in case of more complex models (such as deep convolutional models) where a single prediction requires many more floating operations than relatively compact biliearn recommender models.

%%_______________________________________
%% In MovieLens 1M experiments, our binary representations are within 4\% of the accuracy of the real-valued model, but are over 13 times faster to score and take only 6\% of the memory.
%% ____________________________________

@@

Let $\symUserSet$ be the set of users, and $\symItemSet$ be the set of items. Each user interacts with a number of items $\symUserInteractionSet_i^+$; the set of all remaining items is denoted by $\symUserInteractionSet^-$.

@@

The model is trained using backpropagation, and so we use a smooth approximation to the derivative of the sign function to facilitate training. Following \citet{courbariaux2016binarized}, we define
\begin{equation}
  \frac{d\sign}{dw}=
  \begin{cases}
    w & \text{if}\ \abs{w} \leq 1 \\
    0 & \text{otherwise}.
  \end{cases}
\end{equation}

@@

\section{Conclusion}
While prediction latency is a pressing concern for many recommender systems, we find that the already compact latent factor models do not stand to benefit from using binary latent representations. The sharp drop in representational power exhibited by binary embeddings makes other approaches (such as exact \citep{koenigstein2012efficient} and approximate \citet{shrivastava2014asymmetric} maximum inner product search) more promising avenues when optimizing large-scale ranking.

>>>>

We speculate that binary representations are more useful in case of more complex models (such as deep convolutional models) where a single prediction requires many more floating operations than relatively compact bilinear recommender models.

@@

Let $\symUserSet$ be the set of users, and $\symItemSet$ be the set of items. Each user interacts with a number of items $\symUserInteractionSet^+$; the set of all remaining items is denoted by $\symUserInteractionSet^-$.

@@

The model is trained using backpropagation, and so we use a smooth approximation to the derivative of the sign function to facilitate training. Following \citet{courbariaux2016binarized}, we define
\begin{equation}
  \frac{d\sign}{dw}=
  \begin{cases}
    1 & \text{if}\ \abs{w} \leq 1 \\
    0 & \text{otherwise}.
  \end{cases}
\end{equation}

@@

\section{Conclusion}
While prediction latency is a pressing concern for many recommender systems, we find that the already compact latent factor models do not stand to benefit from using binary latent representations. The sharp drop in representational power exhibited by binary embeddings makes other approaches (such as exact \citep{koenigstein2012efficient} and approximate \citep{shrivastava2014asymmetric} maximum inner product search) more promising avenues when optimizing large-scale ranking.
